\documentclass{article}
\usepackage{import}
\usepackage{preamble}


\begin{document}

\begin{spacing}{1.2}

\centering\huge{Murdock Aubry}\small\\[0.20cm]
\href{mailto:murdock.aubry@mail.utoronto.ca}{\color{blue}email} \big| (705) 994 - 3636 \big| \href{https://github.com/murdock-aubry}{\color{blue}GitHub} \big| \href{https://www.linkedin.com/in/murdock-aubry}{\color{blue}Linkedin} \big| \href{https://murdockaubry.com/}{\color{blue}Website}
\flushleft
\vspace{-0.5cm}

\LARGE{\textbf{Education}}\\
\vspace{-0.2cm}
\noindent\rule{17cm}{0.7pt}
\large{\textbf{University of Toronto}} \hspace{\fill} \small\textbf{June 2024 (Expected)}\\
\normalsize H.B.Sc. Mathematics and Physics Specialist\\
\small\emph{Coursework: Machine learning, Deep learning, numerical analysis, optimization, 
nonlinear mechanics, computational physics, practical physics, real analysis, complex analysis, 
PDEs, linear algebra, probability, statistical analysis, topology, differential geometry, 
quantum mechanics, quantum information, classical mechanics, electromagnetism.}\\[0.20cm]

\LARGE{\textbf{Experience}}\normalsize\\
\vspace{-0.2cm}
\noindent\rule{17cm}{0.7pt}

\textbf{Research Assistant} $ \ \cdot \ $ \small{\textbf{University of Toronto}} \hspace{\fill} \textbf{April 2023 - Present}\\
% \small \textbf{University of Toronto}\\
\normalsize 

Currently conducting research on mathematical computational methods, with a large 
focus placed on numerical integration, differentiation, and numerical solvers of 
differential equations. A large focus is placed on implementing Fortran code for 
these solvers. Supervised by Professor James Bremer from the department 
of mathematics. This work has lead to a 
\href{https://arxiv.org/abs/2308.03288}{\color{blue}preprint}. \\ [0.10cm]

% \begin{itemize}
%     \item Conducted extensive research on numerical integration methods, focusing on optimizing algorithms using Fortran programming language.\\
%     \item Designed and implemented novel numerical integration algorithms, improving accuracy, efficiency, and stability in computational simulations.\\
%     \item Evaluated algorithm performance through rigorous testing, bench-marking, and analysis of real-world applications.
% \end{itemize}

\textbf{Research Assistant} $ \ \cdot \ $ \small{\textbf{University of Toronto}} \hspace{\fill} \textbf{September 2023 - Present}\\
% \small \textbf{University of Toronto}\\
\normalsize 

Working in collaboration with a CERN research team of graduating students at U of T focussed 
on optimizing machine learning algorithms to determine the sensitivity of the DUNE detector 
to detect tau neutrinos. This project is supervised by Professro Nikolina Ilic in the physics departement
in the form of a research course. See \href{https://arxiv.org/abs/2308.03288}{\color{blue}here} 
for up to date progress. \\[0.10cm]


\textbf{Teaching Assistant} $ \ \cdot \ $ \small{\textbf{University of Toronto}} \hspace{\fill} \textbf{September 2023 - Present}\\
% \small \textbf{University of Toronto}\\
\normalsize 

I am a teaching assistant for \href{https://artsci.calendar.utoronto.ca/course/mat244h1}{\color{blue}MAT244}, 
a second year course in ordinary differential equations. The position involves grading, 
exam invigilation, and running three weekly tutorials, each containing over 50 students.\\[0.10cm]


\textbf{Tutor} $ \ \cdot \ $ \small{\textbf{Forest Hill Tutoring}} \hspace{\fill} \textbf{September 2023 - Present}\\
% \small \textbf{University of Toronto}\\
\normalsize 
High school math and physics tutoring, largely focused on helping grade 11 and 12 IB students. 
Develop comprehensive lesson plans, incorporating relevant curriculum materials, practice 
exercises, and interactive teaching methods to engage students and reinforce understanding.\\[0.10cm]



\textbf{Civil Engineering Assistant} $ \ \cdot \ $ \small{\textbf{SKYGRiD}} \hspace{\fill} \textbf{April 2022 - October 2022}\\
% \small \textbf{University of Toronto}\\
\normalsize 

Worked on a 57 storey building in downtown Toronto, assisting the senior and assistant supervisors.
Independently managed construction and renovation of small townhouse in downtown Toronto.
Worked alongside mechanical, civil, and electrical engineers throughout entire construction process.\\[0.20cm]


\LARGE{\textbf{Academia}}\normalsize\\
\vspace{-0.2cm}
\noindent\rule{17cm}{0.7pt}

\textbf{Preprint.} The Levin approach to the numerical calculation of phase functions. Murdock Aubry, James Bremer.
\href{https://arxiv.org/pdf/2308.03288.pdf}{\color{blue}PDF}\\[0.10cm]

\textbf{CUMC Talk 2023.} The Adaptive Levin Method. \\[0.10cm]

\textbf{Online Course.} Deep Learning With PyTorch: Image Segmentation.
\href{https://coursera.org/share/af13e96fd8a6f4c130db6e4bed3a3f1e}{\color{blue}Certificate},
\href{https://colab.research.google.com/drive/10UfARsUTKQkb56pkxxvbH-zTucQkDJEw#scrollTo=seventh-seating}{\color{blue}Code}\\[0.20cm]

\LARGE{\textbf{Technical Skills}}\normalsize \\[0.10cm]
\vspace{-0.2cm}
\noindent\rule{17cm}{0.7pt}

\textbf{Languages.} Python, Fortran, R, HTML, CSS, Bootstrap, \LaTeX .\\[0.10cm]

\textbf{Packages.} PyTorch, TensorFlow, Numpy, Scipy, Pandas. \\[0.10cm]

\textbf{Software.} AutoCAD, macOS, GitHub, Final Cut, Adobe. \\[0.10cm]

\end{spacing}

\end{document}
